### 2025-05-06 evaluating-prediction-accuracy.qmd
20250505 - predictive R-squared

>>>>

Here is an example of estimating predictive $R^2$ with a training and testing data set using the `caret` package [@R-caret].

inTrain <- caret::createDataPartition(
  y = as.factor(mydata$outcomeVariable),
  p = .75, # the proportion of data for the training data set
  list = FALSE
)

training <- mydata[ inTrain,]
testing  <- mydata[-inTrain,]

training_model <- lm(
  outcomeVariable ~ predictorVariable1 + predictorVariable2,
  data = training)

testing_predictions <- predict(
  training_model,
  newdata = testing)

petersenlab::accuracyOverall(
  predicted = testing_predictions,
  actual = testing$outcomeVariable)$rsquared
```
